Assessing primitives performance\\ on multi-stage execution

### 2018-05-07 paper.tex
related work + section 2finish

\cba{TODO!}
To solve this performance bottleneck, the Cog VM allows to redefine primitives on top of its back-end. 
integrated as part of the native code generated.
No switch cost.
No need to reimpl long running code -> direct in Abs assembly, hard to write and maintain, have to be smart to compete with optimized C code.
=> often partial impl for quick to perform prim, for ex, add of 2 int, if overflow just go back to C prim.

>>>>

To solve this performance bottleneck, the Cog VM allows to redefine primitives in Cog's Register Transfer Language (RTL), an abstract assembly which is compiled to native code through Cog's JIT back-end. Such primitives are then generated to native code at runtime when a method annotated with the primitive is compiled to native code. This allows the primitive to be performed in the client stack with the client calling convention, saving register moves and the stack switch dance. Primitives redefined in such way can be entirely or partially redefined. In the later case, only the common cases are re-implemented on top of the JIT back-end, and an unimplemented case happens at runtime, the generated native code calls the C primitive instead, adding overhead only in uncommon cases.
